Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-16 presentations/bsa_2020-07-27/index.Rmd
Update slides
- add background images for selected fern species

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, include = TRUE, eval = TRUE, cache = TRUE, dev = "svg")
```

@@

```{r, load_refs, includ = FALSE, cache = FALSE}
# Set bibliography options
library(RefManageR)
BibOptions(
  ignore.case = TRUE,
  check.entries = FALSE, 
  bib.style = "authoryear", # set style of bibliography as e.g., "Nitta 2020..."
  style = "text" # set style of citations as plain text (no links)
)

@@

- Infer phylogeny with IQ-TREE `r AutoCite(bib, "Nguyen2015")`

@@

- Recently speciation

.small[`r Citet(bib, "Mishler2014")`]
]

@@

.footnote[Trendline: GAM with cubic splines `r NoCite(bib, "Faith1992")`]
---
## Southern islands have high RFD

@@

(Phylogenetic endemism = PD weighted by range size)

@@

.footnote[`r Citet(bib, "Daru2017")`]

@@

@@

@@

@@

@@

@@

- Phylogenetic and functional diversity, phylogenetic endemism highest in Okinawa
]

@@

.small[
```{r, results='asis', echo = FALSE, warning = FALSE, cache = FALSE}
PrintBibliography(bib, start = 1, end = 6)
```
]

@@

.small[
```{r, results='asis', echo = FALSE, warning = FALSE, cache = FALSE}
PrintBibliography(bib, start = 7, end = 12)
```
]

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, include = TRUE, eval = TRUE, cache = TRUE, dev = "svg", dev.args=list(bg="transparent"))
```

@@

```{r, load-refs, includ = FALSE, cache = FALSE}
# Set bibliography options
library(RefManageR)
BibOptions(
  ignore.case = TRUE,
  check.entries = FALSE,
  max.names = 3,
  bib.style = "authoryear", # set style of bibliography as e.g., "Nitta 2020..."
  style = "text" # set style of citations as plain text (no links)
)

@@

- Infer phylogeny with IQ-TREE (Nguyen et al., 2015) `r NoCite(bib, "Nguyen2015")`

@@

- Recent speciation

.small[Mishler et al. (2014) `r NoCite(bib, "Mishler2014")`]
]

@@

.footnote[Trendline: GAM with cubic splines]
---
## Southern islands have high RFD

@@

Phylogenetic endemism = PD weighted by range size (Rosauer et al., 2009) `r NoCite(bib, "Rosauer2009")`

@@

.footnote[`r Citet(bib, c("Daru2017", "Daru2020"))`]

@@

---
background-position: 50% 50%
background-image: url(images/species-background-1.png)
background-size: contain

## Most sites fall into four bioregions

@@

.footnote[`r NoCite(bib, c("Ebihara2016b", "Ebihara2017"))`]

---
background-position: 50% 50%
background-image: url(images/species-background-2.png)
background-size: contain

## Most sites fall into four bioregions

@@

.footnote[`r NoCite(bib, c("Ebihara2016b", "Ebihara2017"))`]

---
background-position: 50% 50%
background-image: url(images/species-background-3.png)
background-size: contain

## Most sites fall into four bioregions

@@

.footnote[`r NoCite(bib, c("Ebihara2016b", "Ebihara2017"))`]

---
background-position: 50% 50%
background-image: url(images/species-background-4.png)
background-size: contain

## Most sites fall into four bioregions

@@

.footnote[`r NoCite(bib, c("Ebihara2016b", "Ebihara2017"))`]

@@

- Phylogenetic and functional diversity, phylogenetic endemism highest in southern islands
]

@@

.small[
```{r, results='asis', echo = FALSE, warning = FALSE, cache = FALSE}
PrintBibliography(bib, start = 1, end = 8)
```
]

@@

.small[
```{r, results='asis', echo = FALSE, warning = FALSE, cache = FALSE}
PrintBibliography(bib, start = 9, end = 16)
```
]
